---
title: "Getting Started: Compute Doodle match probability"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started: Compute Doodle match probability}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  message = FALSE
)
```

```{r setup}
library(doodleproblem)
library(tidyverse)
library(tictoc)
```




# Parameters

```{r}
n_colleagues <- 3
p <- 3
o <- 10
dep <- 0
```


# Doodle match probability


```{r}
prob_doodle_match(n_colleagues = 5,
                  o = 10,
                  p = 3,
                  dep = 0)
```

We can also a somewhat more detailled output by setting `return_prob` to `FALSE`:




```{r}
prob_doodle_match(n_colleagues = 5,
                  o = 10,
                  p = 3,
                  dep = 0,
                  return_prob = FALSE)
```


# Doodle samples 1


```{r cache=TRUE}
smples1 <- doodle_samples(n_colleagues, o, p)
glimpse(smples1)
```

The parameters given to the function call can be found using `attr` afterwards:

```{r}
attr(smples1, "n_colleagues")
attr(smples1, "o")
```


A similar dataset is available as data:

```{r}
data(smples1)
```


# Doodle samples 2

Let's set `dep` to .5:

```{r cache=TRUE}
smples2 <- doodle_samples(n_colleagues, o, p, dep = .5)
glimpse(smples2)
```


A similar dataset is available as data:

```{r}
data(smples2)
```


# Summarize samples

`summarize_smples` is what is finally called in `prob_doodle_match`.


```{r}
summarize_samples(smples1)
```



