---
title: "Sensitivity Analysis 3 - Effect of varying number of picked slots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sensitivity Analysis 3 - Effect of varying number of picked slots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  message = FALSE
)
```


# Setup

```{r setup}
library(doodleproblem)
library(dplyr)
library(ggplot2)
library(tictoc)
```



# Varying number of picked options


For each colleague, the number of picked options is a number randomly drawn from a normal distribution with mean `p` and sd `p_sd`. (Note that for technical reasons, the first colleagues always picks exactly `p` slots currently.)

In other words, the number of `p` varies. 


# Example with non-varying p

```{r}
out <- count_common_slots(n_colleagues = 3,
                          o = 7,
                          p = 3,
                          dep = .5,
                          p_sd = 0)

out
```

As can be seen, the number of picked options remains constant across all colleagues:

```{r}
attr(out, "chosen_options_l")
```


# Example with varying p

```{r}
out2 <- count_common_slots(n_colleagues = 3,
                          o = 7,
                          p = 3,
                          dep = .5,
                          p_sd = 1)

out2
```




As can be seen, the number of picked options remains constant across all colleagues:

```{r}
attr(out2, "chosen_options_l")
```


Of course, the number of picked options influences the probability of finding a match.




# Sensitivity analysis 3


```{r pop-grid3, cache=TRUE, eval = FALSE}
tic()
grid3 <- populate_grid(n_colleagues = 3:5, 
                      o = c(5, 10, 15, 20), 
                      p = c(3, 5), 
                      dep = c(0, .5),
                      p_sd = c(0, 1))
toc()
```




It's quicker to load from disk:

```{r}
data(grid3)
```


# Visualize grid 3a - dep = 0


```{r vis-grid3a, fig.width=9, dpi=300, out.width="100%", fig.asp=1.5}
#undebug(vis_grid2)
grid3a <-
grid3 |> 
  filter(dep == 0)

vis_grid2(grid3a, facet_var_rows = "p_sd", facet_var_cols = "p")
```



# Visualize grid 3b - dep = 0.5


```{r vis-grid3b, fig.width=9, dpi=300, out.width="100%", fig.asp=1.5}
#undebug(vis_grid2)
grid3b <-
grid3 |> 
  filter(dep == 0.5)
vis_grid2(grid3b, facet_var_rows = "p_sd", facet_var_cols = "p")
```
